Towards Transparency and Open Science

### 2023-01-11 manuscript.Rmd
add paper pdfs

# Published Papers

>>>>

# Articles

## A Reproducible Data Analysis Workflow With R Markdown, Git, Make, and Docker

The following article is reprinted from the following source under [Creative Commons Attribution (CC BY) 4.0 International License](https://creativecommons.org/licenses/by/4.0).

Peikert, A., & Brandmaier, A. M. (2021). A Reproducible Data Analysis Workflow With
R Markdown, Git, Make, and Docker. Quantitative and Computational Methods in Behavioral Sciences, 1, e3763. https://doi.org/10.5964/qcmb.3763

\includepdf[pages=-]{papers/workflow.pdf}

## Reproducible Research in R: A Tutorial on How to Do the Same Thing More Than Once

The following article is reprinted from the following source under [Creative Commons Attribution (CC BY) 4.0 International License](https://creativecommons.org/licenses/by/4.0).

Peikert, A., van Lissa, C. J., & Brandmaier, A. M. (2021). Reproducible Research in R: A Tutorial on How to Do the Same Thing More Than Once. *Psych*, *3*(4), 836–867. https://doi.org/10.3390/psych3040053

\includepdf[pages=-]{papers/tutorial.pdf}

## Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

The following article is prepared to be submitted to *Philosophical Psychology*.
The preprint is reprinted here under [Creative Commons Public Domain Dedication (CC0 1.0)](https://creativecommons.org/publicdomain/zero/1.0/).

\includepdf[pages=-]{papers/prereg.pdf}
